---
title: "Getting started with humicon"
author: "Ahmadou Dicko"
date: "2018-12-25"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with humicon}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(humicons)
```

## OCHA Humanitarian icons
The `humicons` package allow you to easily embed OCHA humanitarian icons into Rmarkdown document.

```{r}
humicons::hi("Food-Security")
```

## Customising the icon

You can customize your icons, here are the list of supported options:

* Color `humicons::hi_Food_Security(size = 2)`: `r humicons::hi_Food_Security(color = "#418fde")`
* Size `humicons::hi_Food_Security(size = 2)`: `r humicons::hi_Food_Security(size = 4)`
* Rotation `humicons::hi_Food_Security(rotate = 180)`: `r humicons::hi_Food_Security(rotate = 180)`
* Flip `humicons::hi_Food_Security(flip = "horizontal")`: `r humicons::hi_Food_Security(flip = "horizontal")`
* Animation `humicons::hi_Food_Security(animate = "spin")`: `r humicons::hi_Food_Security(animate = "spin")`
* Fixed width `humicons::hi_Food_Security(fixed_width = TRUE)`: `r humicons::hi_Food_Security(fixed_width = TRUE)`
* Border `humicons::hi_Food_Security(border = TRUE)`: `r humicons::hi_Food_Security(border = TRUE)`
* Pull `humicons::hi_Food_Security(pull = "left")`: `r humicons::hi_Food_Security(pull = "left")`
