---
title: "Getting started with humicon"
author: "Ahmadou Dicko"
date: "2018-12-25"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with humicon}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(humicon)
```

## OCHA Humanitarian icons
The `humicon` package allow you to easily embed OCHA humanitarian icons into Rmarkdown document.

```{r}
humicon::hi("Food-Security")
```

## Customising the icon

You can customize your icons, here are the list of supported options:

* Size `humicon::hi_Food_Security(size = 2)`: `r humicon::hi_Food_Security(size = 2)`
* Rotation `humicon::hi_Food_Security(rotate = 180)`: `r humicon::hi_Food_Security(rotate = 180)`
* Flip `humicon::hi_Food_Security(flip = "horizontal")`: `r humicon::hi_Food_Security(flip = "horizontal")`
* Animation `humicon::hi_Food_Security(animate = "spin")`: `r humicon::hi_Food_Security(animate = "spin")`
* Fixed width `humicon::hi_Food_Security(fixed_width = TRUE)`: `r humicon::hi_Food_Security(fixed_width = TRUE)`
* Border `humicon::hi_Food_Security(border = TRUE)`: `r humicon::hi_Food_Security(border = TRUE)`
* Pull `humicon::hi_Food_Security(pull = "left")`: `r humicon::hi_Food_Security(pull = "left")`
