---
title: "Getting started with humicon"
author: "Ahmadou Dicko"
date: "2018-12-25"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with humicon}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(humicons)
```

## OCHA Humanitarian icons
The `humicons` package allow you to easily embed OCHA humanitarian icons into Rmarkdown document.

```{r}
humicons::humicon_rmd("Food-Security")
```

## Customising the icon

You can customize your icons, here are the list of supported options:

* Color `humicons::humicon_rmd("food-security", color = "#418fde")`: `r humicons::humicon_rmd("food-security", color = "#418fde")`
* Size `humicons::humicon_rmd("food-security", size = 3)`: `r humicons::humicon_rmd("food-security", size = 3)`
* Rotation `humicons::humicon_rmd("food-security", rotate = 180)`: `r humicons::humicon_rmd("food-security", rotate = 180)`
* Flip `humicons::humicon_rmd("food-security", flip = "horizontal")`: `r humicons::humicon_rmd("food-security", flip = "horizontal")`
* Animation `humicons::humicon_rmd("food-security", animate = "spin")`: `r humicons::humicon_rmd("food-security", animate = "spin")`
* Border `humicons::humicon_rmd("food-security", border = TRUE)`: `r humicons::humicon_rmd("food-security", border = TRUE)`
* Pull `humicons::humicon_rmd("food-security", pull = "left")`: `r humicons::humicon_rmd("food-security", pull = "left")`
